\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 & #2 \\
\end{tabular*}}

\begin{document}

% ────────────────────────────────────────────────
%  HEADER
% ────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{ARTUR IASENOVETS}} \\
    \vspace{0.1cm}
    Chongqing, China $\bullet$
    \href{mailto:archee.busy@gmail.com}{archee.busy@gmail.com} $\bullet$
    \href{https://linkedin.com/in/iasenovets}{LinkedIn}
\end{center}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  SUMMARY
% ────────────────────────────────────────────────
\noindent
\textbf{Software Engineer} with more than 3 years of experience building production-grade applications,
including 1 year developing LLM-powered products at an EdTech startup and 6 months interning
at Positive Technologies, a leading Eastern European cybersecurity company. Proficient in Python, Go, and TypeScript,
familiar with Windows and Linux environments, and experienced in security tooling, threat intelligence pipelines,
and end-to-end CI/CD automation. Published research on blockchain query privacy using homomorphic encryption scheme,
cryptographic protocols for searchable encryption, and multi-feed threat intelligence in peer-reviewed journals.

\vspace{0.3cm}

% ────────────────────────────────────────────────
%  EXPERIENCE
% ────────────────────────────────────────────────
\subsection*{\Large Experience}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=0em, itemsep=0.6em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Security Intern}}
        {Remote}
    \headerrow
        {\emph{Positive Technologies --- Leading Eastern European cybersecurity company}}
        {\emph{Aug. 2024 -- Feb. 2025}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Developed \textbf{Python} regex utilities with unit-test coverage for parsing Windows file paths and network configs at the \textbf{MaxPatrol EDR} product team; built a \textbf{Windows Prefetch}-based software allowlist/blocklist checker and a Dockerized \textbf{Telegram bot} for automated compliance monitoring.
        \item Engineered a \textbf{Python} file-processing pipeline for the \textbf{Threat Intelligence} team, fetching malware samples from VX-Underground, storing extracted files in \textbf{S3/MinIO}, and scanning them with \textbf{YARA} rules; packaged the workflow as an \textbf{Airflow DAG} for daily automated processing.
        \item Performed hands-on security analysis as part of the \textbf{SOC} team: investigated attack chains for \textbf{CVE-2020-5902} and \textbf{CVE-2023-38831}, conducted EVTX log forensics with \textbf{Chainsaw}, deobfuscated PowerShell payloads, analyzed malicious \textbf{VBA macros} with oletools, extracted IoCs and mapped TTPs to \textbf{MITRE ATT\&CK}.
    \end{itemize}

    \item
    \headerrow
        {\textbf{Software Engineer}}
        {Remote}
    \headerrow
        {\emph{academai.ru --- AI-powered EdTech startup building personalized LLM learning tools}}
        {\emph{Aug. 2023 -- Aug. 2024}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Designed and delivered an LLM-app generating personalised educational content,
              used in production, using \textbf{Python, Flask, AsyncIO, and Langchain}.
        \item Developed a responsive frontend with \textbf{Next.js, TypeScript, Prisma, and Auth.js},
              ensuring seamless user authentication and consistent UI across the platform.
        \item Reduced deployment friction by building a full \textbf{CI/CD pipeline} via GitHub Actions
              with \textbf{Docker} containerization, cutting release cycles significantly.
    \end{itemize}

    \item
    \headerrow
        {\textbf{Software Developer}}
        {Russia}
    \headerrow
        {\emph{ECP Progress LLC --- Regional manufacturer of high-voltage ceramic capacitors}}
        {\emph{May 2022 -- Aug. 2023}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Designed and developed a full stack warehouse \textbf{QR-inventory system} using
              \textbf{Python and FastAPI}, replacing a manual tracking process entirely.
        \item Conducted personnel interviews with 10+ stakeholders to gather requirements,
              reducing ambiguity and aligning the solution with real operational needs.
        \item Owned the complete development lifecycle: backlogging, architecture design,
              code reviews, testing, debugging, and production deployment.
    \end{itemize}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  SKILLS
% ────────────────────────────────────────────────
\subsection*{\Large Skills}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, noitemsep]
    \renewcommand\labelitemi{}
    \item \textbf{Languages:} Python, Go, TypeScript, JavaScript, SQL, NoSQL
    \item \textbf{Frameworks / Libraries:} FastAPI, Flask, Next.js, React, Redux, Langchain, Prisma, Auth.js, Hardhat, Web3.py
    \item \textbf{Tools:} Docker, Nginx, Hyperledger Fabric, Git, GitHub Actions, AsyncIO, S3, Airflow, YARA, Chainsaw
    \item \textbf{Language Skills:}
    \href{https://certs.duolingo.com/751e0ef152565727b6d5fd909699ceaa}{English C1},
    \href{https://admin.chinesetest.cn/queryScore.do?sid=c2tActR9Wb%2704b861aefbdc5e9fd0b44afa717d08cbceb0720e582ce25f%2724d7sWsQ5nVUQSwD}{Chinese HSK3},
    Russian native
\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  EDUCATION
% ────────────────────────────────────────────────
\subsection*{\Large Education}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.4em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Chongqing University of Posts and Telecommunications}}
        {Chongqing, China}
    \headerrow
        {\emph{M.S. Network \& Information Security}}
        {\emph{Sept. 2024 -- Present}}

    \item
    \headerrow
        {\textbf{Ukhta State Technical University}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies} \quad \textbf{GPA: 4.5/5.0}}
        {\emph{March. 2022 -- June 2024}}

    \item
    \headerrow
        {\textbf{St. Petersburg State University of Telecommunications named after Prof. M.A. Bonch-Bruevich}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies} \quad \textbf{GPA: 4.2/5.0}}
        {\emph{Sept. 2020 -- March 2022}}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  PUBLICATIONS
% ────────────────────────────────────────────────
\subsection*{\Large Publications}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.5em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \headerrow
        {\textbf{MFCTIIF: Multi-Feed Cyber Threat Intelligence Integration Framework}}
        {\emph{Jan. 2026}}
    \headerrow
        {\emph{Iasenovets A.V., Tang F. --- International Research Journal, No.\,1 (163)}}
        {\href{https://doi.org/10.60797/IRJ.2026.163.57}{DOI}}
    \vspace{0.1em}
    {\small Proposed a modular framework aggregating heterogeneous CTI feeds (MalwareBazaar, VirusTotal, APT ETDA), performing metadata enrichment, synonym resolution, and automated threat-level classification; evaluated on 100 malware samples with ~15--17s end-to-end latency.}

    \item
    \headerrow
        {\textbf{EVMK-SSE: Efficient and Verifiable Multi-Keyword Symmetric Searchable Encryption}}
        {\emph{Dec. 2025}}
    \headerrow
        {\emph{Zhu H., Tang F., Qin W., Shan J., Wang P., Iasenovets A. --- J. King Saud Univ. Comput. Inf. Sci.}}
        {\href{https://doi.org/10.1007/s44443-025-00405-8}{DOI}}
    \vspace{0.1em}
    {\small Proposed EVMK-SSE, an efficient and verifiable multi-keyword SSE scheme replacing DH-OPRF with a lightweight OT-based client-independent relaxed OPRF, reducing computational overhead while maintaining strong privacy guarantees for outsourced cloud databases.}

    \item
    \headerrow
        {\textbf{Bringing Private Reads to Hyperledger Fabric via Private Information Retrieval}}
        {\emph{Nov. 2025}}
    \headerrow
        {\emph{Iasenovets A., Tang F., Zhu H., Wang P., Liu L. --- arXiv preprint (submitted to IEEE)}}
        {\href{https://arxiv.org/abs/2511.02656}{arXiv:2511.02656}}
    \vspace{0.1em}
    {\small Proposed and implemented a BGV homomorphic encryption-based PIR mechanism natively in Hyperledger Fabric chaincode, enabling private world-state reads without modifying Fabric's core architecture; achieved 113 ms end-to-end latency and $\sim$2 MB peer traffic per query across a multi-channel prototype.}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  ACHIEVEMENTS
% ────────────────────────────────────────────────
\subsection*{\Large Achievements}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.4em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \headerrow
        {\textbf{5 Science Conferences}}
        {\emph{Apr. 2022 -- Apr. 2023}}
    Won \textbf{3 consecutive first places} in paper evaluations across various scientific conferences.

    \item
    \headerrow
        {\textbf{SberStudent Product Sprint}}
        {\emph{June 2023 -- Nov. 2023}}
    Advanced \href{https://youknow.academai.ru}{\textbf{youknow}} (academai.ru) --- an LLM-powered personalized course generator --- to the finalist stage and presented the product MVP at the \textbf{regional demo in St.\ Petersburg} out of hundreds of student teams nationwide.

    \item
    \headerrow
        {\textbf{iTechPred Product Sprint}}
        {\emph{Oct. 2023 -- Nov. 2023}}
    Pitched \href{https://youknow.academai.ru}{\textbf{youknow}} as an EdTech product at Petrozavodsk State University's student sprint, reaching the finals and presenting at the regional online demo day.

    \item
    \headerrow
        {\textbf{MIPT \& Sber Phystech GigaChat Challenge Hackathon}}
        {\emph{Dec. 2023}}
    Developed \href{https://youknow.academai.ru}{\textbf{youknow}} (academai.ru) --- an LLM-app generating personalized educational courses --- using \textbf{GigaChat} and \textbf{Kandinsky} APIs within a 48-hour hackathon sprint.

    \item
    \headerrow
        {\textbf{Kaspersky Cyberimmune Development Hackathon 2.0}}
        {\emph{Oct. 2023 -- Dec. 2023}}
    Contributed to the design of a \textbf{cyber-attack resistant architecture} for an on-board drone inspector system protecting critical infrastructure.

\end{itemize}

\end{document}