\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 & #2 \\
\end{tabular*}}

\begin{document}

% ────────────────────────────────────────────────
%  HEADER
% ────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{ARTUR IASENOVETS}} \\
    \vspace{0.1cm}
    Chongqing, China $\bullet$
    \href{mailto:archee.busy@gmail.com}{archee.busy@gmail.com} $\bullet$
    \href{https://linkedin.com/in/iasenovets}{LinkedIn} $\bullet$
    \href{https://orcid.org/0009-0008-0008-3746}{ORCID} $\bullet$
    \href{https://iasenovets.github.io/}{Portfolio}
\end{center}

\vspace{0.15cm}

% ────────────────────────────────────────────────
%  RESEARCH PROFILE
% ────────────────────────────────────────────────
\noindent
\textbf{Applied Cryptography Researcher} focused on fully homomorphic encryption (FHE),
private information retrieval (PIR), and privacy-preserving systems. M.S. student in Network \&
Information Security at Chongqing University of Posts and Telecommunications. Hands-on
experience implementing BGV-based PIR in Hyperledger Fabric using Lattigo and CKKS-based
encrypted aggregation for federated reinforcement learning using TenSEAL, PyTorch, and NumPy.
Research background spans FHE, PIR, searchable encryption, cyber threat intelligence, and
privacy-preserving computation, with emphasis on working prototypes, parameter selection, and
empirical evaluation.

\vspace{0.15cm}

\noindent\textbf{Research Interests:} Fully Homomorphic Encryption, Private Information Retrieval,
Privacy-Preserving Machine Learning, Secure Aggregation, Blockchain Privacy, Cyber Threat Intelligence

\vspace{0.3cm}

% ────────────────────────────────────────────────
%  EDUCATION
% ────────────────────────────────────────────────
\subsection*{\Large Education}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=1em, itemsep=0.4em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Chongqing University of Posts and Telecommunications}}
        {Chongqing, China}
    \headerrow
        {\emph{M.S. Network \& Information Security \quad Supervisor: \href{https://faculty.cqupt.edu.cn/tangfei/en/index.htm}{Prof. Tang Fei}}}
        {\emph{Sept. 2024 -- Present}}
        {\emph{GPA: 3.9/4.0}}

    \item
    \headerrow
        {\textbf{Ukhta State Technical University}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies}}
        {\emph{March 2022 -- June 2024}}
        {\emph{GPA: 4.5/5.0 (3.6/4.0)}}

    \item
    \headerrow
        {\textbf{St. Petersburg State University of Telecommunications named after Prof. M.A. Bonch-Bruevich}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies}}
        {\emph{Sept. 2020 -- March 2022}}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  PUBLICATIONS AND MANUSCRIPTS
% ────────────────────────────────────────────────
\subsection*{\Large Publications \& Manuscripts}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.5em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \headerrow
        {\textbf{Bringing Private Reads to Hyperledger Fabric via Private Information Retrieval}}
        {\emph{Nov. 2025}}
    \headerrow
        {\emph{Iasenovets A., Tang F., Zhu H., Wang P., Liu L. --- arXiv preprint (submitted to IEEE)}}
        {\href{https://arxiv.org/abs/2511.02656}{arXiv:2511.02656}}
    \vspace{0.1em}
    {\small Proposed and implemented a BGV homomorphic encryption-based PIR mechanism natively in Hyperledger Fabric chaincode, enabling private world-state reads without modifying Fabric's core architecture; achieved 113 ms end-to-end latency and $\sim$2 MB peer traffic per query across a multi-channel prototype.}

    \item
    \headerrow
        {\textbf{EVMK-SSE: Efficient and Verifiable Multi-Keyword Symmetric Searchable Encryption}}
        {\emph{Dec. 2025}}
    \headerrow
        {\emph{Zhu H., Tang F., Qin W., Shan J., Wang P., Iasenovets A. --- J. King Saud Univ. Comput. Inf. Sci.}}
        {\href{https://doi.org/10.1007/s44443-025-00405-8}{DOI}}
    \vspace{0.1em}
    {\small Proposed EVMK-SSE, replacing DH-OPRF with a lightweight OT-based client-independent relaxed OPRF in a multi-keyword SSE scheme, reducing computational overhead while maintaining strong privacy guarantees for outsourced encrypted cloud databases.}

    \item
    \headerrow
        {\textbf{MFCTIIF: Multi-Feed Cyber Threat Intelligence Integration Framework}}
        {\emph{Jan. 2026}}
    \headerrow
        {\emph{Iasenovets A.V., Tang F. --- International Research Journal, No.\,1 (163)}}
        {\href{https://doi.org/10.60797/IRJ.2026.163.57}{DOI}}
    \vspace{0.1em}
    {\small Proposed a modular CTI framework aggregating heterogeneous feeds (MalwareBazaar, VirusTotal, APT ETDA), performing metadata enrichment, synonym resolution, and automated threat-level classification; evaluated on 100 malware samples with $\sim$15--17s end-to-end latency.}

    \item
    \headerrow
        {\textbf{Adaptive Privacy-Aware Federated Reinforcement Learning with Trust-Weighted Secure Aggregation}}
        {\emph{2026}}
    \headerrow
        {\emph{Manuscript in preparation --- second author}}
        {}
    \vspace{0.1em}
    {\small Contributing CKKS-based encrypted aggregation using TenSEAL with chunked model-update encoding for privacy-preserving federated reinforcement learning; implementation uses PyTorch and NumPy for local learning/evaluation and TenSEAL for encrypted aggregation.}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  SELECTED RESEARCH PROJECTS
% ────────────────────────────────────────────────
\subsection*{\Large Selected Research Projects}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.6em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \textbf{BGV-Based Private Information Retrieval for Hyperledger Fabric}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Implemented a single-server HE-PIR prototype using BGV over packed CTI records, with client-side encrypted selection vectors and chaincode-side ciphertext-plaintext evaluation.
        \item Designed fixed-window record packing, parameter/capacity checks, and client-side decoding for privacy-preserving reads from Fabric world state.
        \item Evaluated end-to-end latency, peer-side evaluation time, network traffic, storage overhead, and parameter/capacity constraints across multiple Fabric channels.
        \item \textbf{Technologies:} Go, Lattigo, Hyperledger Fabric, Docker, BGV, PIR, RLWE-based HE.
    \end{itemize}

    \item
    \textbf{CKKS-Based Encrypted Aggregation for Federated Reinforcement Learning}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Implemented CKKS-encrypted model-update aggregation for federated reinforcement learning using TenSEAL, PyTorch, and NumPy.
        \item Used chunking to encode model-update vectors into encrypted CKKS payloads for aggregation.
        \item Compared plaintext, differential privacy, trust-weighted, HE, and combined HE+DAPI execution paths for network-defense learning.
        \item \textbf{Technologies:} Python, TenSEAL, PyTorch, NumPy, CKKS, federated learning, reinforcement learning.
    \end{itemize}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  TECHNICAL SKILLS
% ────────────────────────────────────────────────
\subsection*{\Large Technical Skills}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, noitemsep]
    \renewcommand\labelitemi{}
    \item \textbf{Cryptography:} Fully Homomorphic Encryption, BGV, CKKS, PIR, searchable encryption, OPRF/OT-based constructions, differential privacy, secure aggregation, RLWE/LWE-based security assumptions
    \item \textbf{FHE Libraries:} Lattigo, Microsoft SEAL, TenSEAL, OpenFHE; familiar with TFHE and Concrete documentation
    \item \textbf{Programming:} Python, Go, TypeScript, JavaScript, SQL
    \item \textbf{ML / Data:} PyTorch, NumPy, federated learning, reinforcement learning, CIC-IDS2017-style intrusion detection workflows
    \item \textbf{Systems / Security:} Hyperledger Fabric, Docker, GitHub Actions, S3/MinIO, Airflow, YARA, Chainsaw, MITRE ATT\&CK
    \item \textbf{Language Skills:}
    \href{https://certs.duolingo.com/751e0ef152565727b6d5fd909699ceaa}{English C1},
    \href{https://admin.chinesetest.cn/queryScore.do?sid=c2tActR9Wb%2704b861aefbdc5e9fd0b44afa717d08cbceb0720e582ce25f%2724d7sWsQ5nVUQSwD}{Chinese HSK3},
    Russian native
\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  RESEARCH EXPERIENCE
% ────────────────────────────────────────────────
\subsection*{\Large Research Experience}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=0em, itemsep=0.6em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Graduate Student Researcher}}
        {Chongqing, China}
    \headerrow
        {\emph{Chongqing University of Posts and Telecommunications --- Applied Cryptography Group}}
        {\emph{Sept. 2024 -- Present}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Designed and implemented BGV-based private information retrieval for Hyperledger Fabric using Lattigo, including packed plaintext encoding, encrypted query generation, ciphertext-plaintext evaluation, and client-side decoding.
        \item Implemented CKKS-based encrypted aggregation for federated reinforcement learning using TenSEAL, PyTorch, and NumPy, including chunked model-update encoding.
        \item Evaluated privacy-preserving prototypes using latency, communication volume, storage overhead, ciphertext expansion, and parameter/capacity constraints.
        \item Contributed to research papers on FHE-based PIR, searchable encryption, cyber threat intelligence, and privacy-preserving federated learning.
        \item Participating in weekly research seminars, paper reviews, and collaborative research discussions within the group.
    \end{itemize}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  PROFESSIONAL EXPERIENCE
% ────────────────────────────────────────────────
\subsection*{\Large Professional Experience}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=0em, itemsep=0.6em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Security Intern}}
        {Remote}
    \headerrow
        {\emph{Positive Technologies --- Leading Eastern European cybersecurity company}}
        {\emph{Aug. 2024 -- Feb. 2025}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Developed Python utilities for the MaxPatrol EDR product team, including regex-based Windows path/network configuration parsing, unit-test coverage, and a Windows Prefetch-based software allowlist/blocklist checker.
        \item Engineered a Python malware-processing pipeline for the Threat Intelligence team, fetching samples from VX-Underground, storing artifacts in S3/MinIO, scanning with YARA rules, and packaging the workflow as an Airflow DAG.
        \item Performed SOC analysis on CVE-2020-5902 and CVE-2023-38831 attack chains, including EVTX log forensics with Chainsaw, PowerShell deobfuscation, VBA macro analysis with oletools, IoC extraction, and MITRE ATT\&CK mapping.
    \end{itemize}

    \item
    \headerrow
        {\textbf{Software Engineer}}
        {Remote}
    \headerrow
        {\emph{academai.ru --- AI-powered EdTech startup under Sberbank's Accelerator program}}
        {\emph{Aug. 2023 -- Aug. 2024}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Built a Flask REST API backend where each endpoint encapsulates a structured system prompt, orchestrating LLM calls via Langchain to generate individual course components on demand.
        \item Developed a responsive frontend with Next.js, TypeScript, Prisma, and Auth.js, ensuring seamless authentication and consistent UI across the platform.
        \item Reduced deployment friction by building a CI/CD pipeline via GitHub Actions with Docker containerization.
    \end{itemize}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  HONORS AND ACHIEVEMENTS
% ────────────────────────────────────────────────
\subsection*{\Large Honors \& Achievements}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.4em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \headerrow
        {\textbf{Chinese Government Scholarship for Graduate Studies}}
        {\emph{Sept. 2024 -- Aug. 2027}}
    Awarded a full scholarship by the Chinese government for the entire duration of the M.S. program at CQUPT.

    \item
    \headerrow
        {\textbf{5 Science Conferences}}
        {\emph{Apr. 2022 -- Apr. 2023}}
    Won 3 consecutive first places in paper evaluations across various scientific conferences while at USTU.

    \item
    \headerrow
        {\textbf{Kaspersky Cyberimmune Development Hackathon 2.0}}
        {\emph{Dec. 2023}}
    Participated in Kaspersky's Cyberimmunity Hackathon in Fall 2023, placing 11th out of 100+ teams.

    \item
    \headerrow
        {\textbf{MIPT \& Sber Phystech GigaChat Challenge Hackathon}}
        {\emph{Dec. 2023}}
    Developed an LLM application for generating personalized educational courses using Sberbank's GigaChat and Kandinsky APIs within a 48-hour sprint; later presented at the regional final demo day.

\end{itemize}

\end{document}
