\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 & #2 \\
\end{tabular*}}

\begin{document}

% ────────────────────────────────────────────────
%  HEADER
% ────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{ARTUR IASENOVETS}} \\
    \vspace{0.1cm}
    Chongqing, China $\bullet$
    \href{mailto:archee.busy@gmail.com}{archee.busy@gmail.com} $\bullet$
    \href{https://linkedin.com/in/iasenovets}{LinkedIn} $\bullet$
    \href{https://orcid.org/0009-0008-0008-3746}{ORCID} $\bullet$
    \href{https://iasenovets.github.io/}{Portfolio}
\end{center}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  SUMMARY
% ────────────────────────────────────────────────
\noindent
\textbf{Graduate Student Researcher} in Network \& Information Security at Chongqing University of Posts
and Telecommunications, with a background in applied cryptography, software engineering, and
security engineering. Submitted 3 research papers on homomorphic encryption-based
Private Information Retrieval, verifiable Symmetric Searchable Encryption, and multi-feed Cyber
Threat Intelligence. Interested in applying FHE schemes and cryptographic constructions in
novel system contexts, with hands-on experience in security research through an internship
at Positive Technologies and software engineering via previous work at an EdTech startup.

\vspace{0.15cm}

\noindent\textbf{Research Interests:} Homomorphic Encryption, Privacy-Enhancing Technologies,
Threat Intelligence, Blockchain

\vspace{0.3cm}

% ────────────────────────────────────────────────
%  EDUCATION
% ────────────────────────────────────────────────
\subsection*{\Large Education}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=1em, itemsep=0.4em]
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Chongqing University of Posts and Telecommunications}}
        {Chongqing, China}
    \headerrow
        {\emph{M.S. Network \& Information Security \quad Supervisor: \href{https://faculty.cqupt.edu.cn/tangfei/en/index.htm}{Prof. Tang Fei}}}
        {\emph{Sept. 2024 -- Present}}
        {\emph{GPA: (3.9/4.0)}}

    \item
    \headerrow
        {\textbf{Ukhta State Technical University}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies}}
        {\emph{March 2022 -- June 2024}}
        {\emph{GPA: 4.5/5.0 (3.6/4.0)}}

    \item
    \headerrow
        {\textbf{St. Petersburg State University of Telecommunications named after Prof. M.A. Bonch-Bruevich}}
        {Russia}
    \headerrow
        {\emph{B.S. Information Systems and Technologies}}
        {\emph{Sept. 2020 -- March 2022}}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  PUBLICATIONS
% ────────────────────────────────────────────────
\subsection*{\Large Publications}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.5em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item
    \headerrow
        {\textbf{Bringing Private Reads to Hyperledger Fabric via Private Information Retrieval}}
        {\emph{Nov. 2025}}
    \headerrow
        {\emph{Iasenovets A., Tang F., Zhu H., Wang P., Liu L. --- arXiv preprint (submitted to IEEE)}}
        {\href{https://arxiv.org/abs/2511.02656}{arXiv:2511.02656}}
    \vspace{0.1em}
    {\small Proposed and implemented a BGV homomorphic encryption-based PIR mechanism natively in Hyperledger Fabric chaincode, enabling private world-state reads without modifying Fabric's core architecture; achieved 113 ms end-to-end latency and $\sim$2 MB peer traffic per query across a multi-channel prototype.}

    \item
    \headerrow
        {\textbf{EVMK-SSE: Efficient and Verifiable Multi-Keyword Symmetric Searchable Encryption}}
        {\emph{Dec. 2025}}
    \headerrow
        {\emph{Zhu H., Tang F., Qin W., Shan J., Wang P., Iasenovets A. --- J. King Saud Univ. Comput. Inf. Sci.}}
        {\href{https://doi.org/10.1007/s44443-025-00405-8}{DOI}}
    \vspace{0.1em}
    {\small Proposed EVMK-SSE, replacing DH-OPRF with a lightweight OT-based client-independent relaxed OPRF in a multi-keyword SSE scheme, reducing computational overhead while maintaining strong privacy guarantees for outsourced encrypted cloud databases.}

    \item
    \headerrow
        {\textbf{MFCTIIF: Multi-Feed Cyber Threat Intelligence Integration Framework}}
        {\emph{Jan. 2026}}
    \headerrow
        {\emph{Iasenovets A.V., Tang F. --- International Research Journal, No.\,1 (163)}}
        {\href{https://doi.org/10.60797/IRJ.2026.163.57}{DOI}}
    \vspace{0.1em}
    {\small Proposed a modular CTI framework aggregating heterogeneous feeds (MalwareBazaar, VirusTotal, APT ETDA), performing metadata enrichment, synonym resolution, and automated threat-level classification; evaluated on 100 malware samples with $\sim$15--17s end-to-end latency.}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  SKILLS
% ────────────────────────────────────────────────
\subsection*{\Large Skills}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, noitemsep]
    \renewcommand\labelitemi{}
    \item \textbf{Languages:} Python, Go, TypeScript, JavaScript, SQL, NoSQL
    \item \textbf{Frameworks / Libraries:} Lattigo, Microsoft SEAL, FastAPI, Langchain, Hardhat, Web3.py
    \item \textbf{Tools:} LWE-Estimator, Hyperledger Fabric, Git, Nginx, Docker, S3, Airflow, YARA, Chainsaw
    \item \textbf{Language Skills:}
    \href{https://certs.duolingo.com/751e0ef152565727b6d5fd909699ceaa}{English C1},
    \href{https://admin.chinesetest.cn/queryScore.do?sid=c2tActR9Wb%2704b861aefbdc5e9fd0b44afa717d08cbceb0720e582ce25f%2724d7sWsQ5nVUQSwD}{Chinese HSK3},
    Russian native
\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  EXPERIENCE
% ────────────────────────────────────────────────
\subsection*{\Large Experience}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=0em, itemsep=0.6em]
    \parskip=0.1em

    % --- Research role ---
    \item
    \headerrow
        {\textbf{Graduate Student Researcher}}
        {Chongqing, China}
    \headerrow
        {\emph{Chongqing University of Posts and Telecommunications --- Applied Cryptography Group}}
        {\emph{Sept. 2024 -- Present}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Designed and implemented a BGV homomorphic encryption-based PIR scheme in Go using Lattigo, integrated natively into Hyperledger Fabric chaincode.
        \item Submitted 3 research papers spanning homomorphic encryption, searchable encryption, and cyber threat intelligence, including one published in a peer-reviewed journal.
        \item Contributing to lab grant and project work in privacy-preserving computation and applied cryptography.
        \item Participating in weekly research seminars, paper reviews, and collaborative research discussions within the group.
    \end{itemize}

    % --- PT ---
    \item
    \headerrow
        {\textbf{Security Intern}}
        {Remote}
    \headerrow
        {\emph{Positive Technologies --- Leading Eastern European cybersecurity company}}
        {\emph{Aug. 2024 -- Feb. 2025}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Developed Python regex utilities with unit-test coverage for parsing Windows file paths and network configs at the MaxPatrol EDR product team; built a Windows Prefetch-based software allowlist/blocklist checker and a Dockerized Telegram bot for automated compliance monitoring.
        \item Engineered a Python malware-processing pipeline for the Threat Intelligence team, fetching samples from VX-Underground, storing artifacts in S3/MinIO, and scanning with YARA rules; packaged as an Airflow DAG for daily automated ingestion.
        \item Performed hands-on security analysis as part of the SOC team: investigated attack chains for CVE-2020-5902 and CVE-2023-38831, conducted EVTX log forensics with Chainsaw, deobfuscated PowerShell payloads, analyzed malicious VBA macros with oletools, extracted IoCs and mapped TTPs to MITRE ATT\&CK.
    \end{itemize}

    % --- academai ---
    \item
    \headerrow
        {\textbf{Software Engineer}}
        {Remote}
    \headerrow
        {\emph{academai.ru --- AI-powered EdTech startup under Sberbank's Accelerator program}}
        {\emph{Aug. 2023 -- Aug. 2024}}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em]
        \renewcommand\labelitemi{$\bullet$}
        \item Built a Flask REST API backend where each endpoint encapsulates a structured system prompt, 
        orchestrating LLM calls via Langchain to generate individual course components on demand.
        \item Developed a responsive frontend with Next.js, TypeScript, Prisma, and Auth.js,
              ensuring seamless user authentication and consistent UI across the platform.
        \item Reduced deployment friction by building a full CI/CD pipeline via GitHub Actions
              with Docker containerization, cutting release cycles significantly.
    \end{itemize}

\end{itemize}

\vspace{0.2cm}

% ────────────────────────────────────────────────
%  ACHIEVEMENTS
% ────────────────────────────────────────────────
\subsection*{\Large Achievements}
\vspace{-0.5em}
\hrule
\vspace{0.3em}

\begin{itemize}[leftmargin=0em, itemsep=0.4em]
    \parskip=0.1em
    \renewcommand\labelitemi{}

    \item 
    \headerrow
        {\textbf{Chinese Government Scholarship for Graduate Studies}}
        {\emph{Sept. 2024 -- Aug. 2027}}
    Awarded a full scholarship by the Chinese government for the entire duration of my master's program at CQUPT.

    \item
    \headerrow
        {\textbf{5 Science Conferences}}
        {\emph{Apr. 2022 -- Apr. 2023}}
    Won 3 consecutive first places in paper evaluations across various scientific conferences while at USTU.

    \item
    \headerrow
        {\textbf{Kaspersky Cyberimmune Development Hackathon 2.0}}
        {\emph{Dec. 2023}}
    Participated in the Kaspersky’s Cyberimmunity Hackathon in Fall 2023, placed 11th out of 100+ teams.

    \item
    \headerrow
        {\textbf{MIPT \& Sber Phystech GigaChat Challenge Hackathon}}
        {\emph{Dec. 2023}}
    Developed an LLM-app generating personalized educational courses (\href{https://youknow.academai.ru}{youknow})
    using Sberbank's GigaChat and Kandinsky APIs within a 48-hour sprint, later presented on the regional final demo day.

\end{itemize}

\end{document}